Report on Late Winter2013 Production: Image Differencing

### 2013-03-29 W13report.tex
Cleaning up section titles since we're getting close.

\subsection{Algorithm and Background {\bf ANDYB}}

@@

\section{Input Data {\bf ANDYC}}

@@

\subsection{Pipeline Implementation {\bf ANDYB}}

@@

\subsection{Improvements to Measurement {\bf RUSS} \label{sec-meas}}

@@

\subsubsection{Mean Squared Error {\bf SIMON}}

@@

\subsubsection{Reduced $\chi^2$ {\bf SIMON}}

\section{Production Runs {\bf ANDYB}}

@@

\subsection{Theoretical {\bf ANDYC}\label{sec-analyticfp}}

\subsection{Empirical {\bf ANDYB}}

@@

\subsection{Effect of Uncertainty on Measured ${S}\over{N}$ {\bf SIMON}}

@@

\subsection{Number of KernelCandidates {\bf ANDYB}}

@@

\subsection{Registration Errors {\bf ANDYB}}

@@

\subsubsection{Coordinate RMS {\bf ANDYB}}

@@

\subsubsection{Coordinate Offsets {\bf ANDYB}}

@@

\subsection{Variance Misestimation {\bf ANDYB/SIMON}}

@@

\subsection{Correlation with KernelCandidate Statistics {\bf ANDYB}}

@@

\section{Results: Measurement {\bf ANDYB}}

@@

\section{Results: Computational Performance {\bf ANDYB}}

@@

\section{Outstanding Issues {\bf SIMON}}
We ran into several issues during this production that required work--arounds.  
In some cases we did not have the time to drill all the way down
to the root cause.  We itemize these issues here so that they may be addressed 
as part of the Summer 2013 work.

>>>>

\subsection{Algorithm and Background}

@@

\section{Input Data}

@@

\subsection{Pipeline Implementation}

@@

\subsection{Improvements to Measurement \label{sec-meas}}

@@

\subsubsection{Mean Squared Error}

@@

\subsubsection{Reduced $\chi^2$}

\section{Production Runs}

@@

\subsection{Theoretical \label{sec-analyticfp}}

\subsection{Empirical}

@@

\subsection{Effect of Uncertainty on Measured ${S}\over{N}$}

@@

\subsection{Number of KernelCandidates}

@@

\subsection{Registration Errors}

@@

\subsubsection{Coordinate RMS}

@@

\subsubsection{Coordinate Offsets}

@@

\subsection{Variance Misestimation}

@@

\subsection{Correlation with KernelCandidate Statistics}

@@

\section{Results: Measurement}

@@

\section{Results: Computational Performance}

@@

\section{Outstanding Issues}
We ran into several issues during this production that required work--arounds.  
In some cases we did not have the time to drill all the way down
to the root cause.  We itemize these issues here so that they may be addressed 
as part of the Summer 2013 work.
